Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-12-14 chapters/chapter01.tex
cover v3

The Bayesian evolutionary analysis by sampling trees (BEAST) software \citep{Drummond2012}, to which our research group contributes, integrates many of the advances described in Subsections~\ref{sub:epidemiology}-\ref{sub:molecular_clock}.
BEAST is set in a Bayesian statistical framework, meaning that it combines the data likelihood (see Subsection~\ref{sub:likelihood}) with prior knowledge (see Subsection~\ref{sec:bayesian_inference}), and generates posterior samples using MCMC (see Subsection~\ref{sub:mcmc}).

>>>>

The Bayesian evolutionary analysis by sampling trees (BEAST) software \citep{Drummond2012}, to which our research group contributes, integrates many of the advances described in Subsections~\ref{sub:epidemiology}-\ref{sub:molecular_clock}.
BEAST is set in a Bayesian statistical framework, meaning that it combines the data likelihood (see Subsection~\ref{sub:likelihood}) with prior knowledge (see Section~\ref{sec:bayesian_inference}), and generates posterior samples using MCMC (see Subsection~\ref{sub:mcmc}).

### 2014-12-14 chapters/chapter06.tex
cover v3

\begin{figure}[H]
\centering
\includegraphics[scale=0.2]{moore}
\caption{
{ \footnotesize 
{\bf Performance gains of a numerical code benchmarked on a single CPU core over the course of 15 years \citep{Turek1999}.}
Last two years have seen only a marginal speed-up, and correspond to the shift to multicore architectures.
} % END: footnotesize
}
\label{fig:moore}
\end{figure}

@@

Complex, biologically-realistic models that target this information also bring about new computational challenges.
Models with large state spaces, such as codon models discussed in Subsection~\ref{sub:dpp} are an example of such a challenge.
More research will be needed to mitigate the imminent computational burdens that come with novel modeling approaches and high-throughput sequencing. 
This will open up new opportunities to analyze data in almost real time, and by coupling molecular sequence data with geographical information, to trace the spread of emerging epidemics and instantly identify potential outbreak locations well as the drivers of viral spread.  
Although it is hard to make any specific predictions, it will be very interesting to see where the future will lead to at the cross-section of data-plenty and high-performance computing and how this will advance infectious disease research.

>>>>

\begin{figure}[H]
\centering
\includegraphics[scale=0.2]{moore}
\caption{
{ \footnotesize 
{\bf Performance gains of a numerical code benchmarked on a single CPU core over the course of 15 years (PDE solver FeatFlow, \citep{Turek1999}).}
Last two years have seen only a marginal speed-up, and correspond to the shift to multicore architectures.
} % END: footnotesize
}
\label{fig:moore}
\end{figure}

@@

Complex, biologically-realistic models that target this information also bring about new computational challenges.
Models with large state spaces, such as codon models discussed in Subsection~\ref{sub:dpp} are an example of such a challenge.
More research will be needed to mitigate the imminent computational burdens that come with novel modeling approaches and high-throughput sequencing. 
This will open up new opportunities to analyze data in almost real time, and by coupling molecular sequence data with geographical information, to trace the spread of emerging epidemics and instantly identify potential outbreak locations as well as the drivers of viral spread.  
Although it is hard to make any specific predictions, it will be very interesting to see where the future will lead to at the cross-section of data-plenty and high-performance computing and how this will advance infectious disease research.
